Bootstrapping Domain Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-02-08 paper.tex
smaller learning curve figures
reworded slightly confusing sentence in abstract

\begin{abstract}
  Successful  approaches to program induction require a
  hand-engineered  domain-specific languaget (DSL),
  constraining the space of allowed programs and imparting
  prior knowledge of the domain.
  We contribute a program learning algorithm
  that learns the DSL called \system,
which infers
  a DSL 
  and trains a neural network to
  efficiently search for programs in the learned DSL.
  We use our model to build circuits,
  edit strings, do symbolic regression,
  and synthesize Lisp-style functions on lists,
  in each case showing that
  \system learns a domain-specific vocabulary for expressing programs.

@@

\begin{figure}\centering
\includegraphics[width = 7cm]{figures/regression.eps}
  \includegraphics[width = 7cm]{figures/list.eps}
  \includegraphics[width = 7cm]{figures/textLearningCurve.eps}
  \includegraphics[width = 7cm]{figures/circuitLearningCurve.eps}  
  \caption{Learning curves for \system both with (blue) and without (red) the recognition model as the frontier size is varied (solid/dashed/dotted lines).}\label{learningCurves} 
\end{figure}

\pagebreak
 \section{Related Work}
 Our work is far from the first to learn to learn programs,
 an  idea that goes back to Solomonoff~\cite{solomonoff1989system}:

>>>>

\begin{abstract}
  Successful approaches to program induction require a
  hand-engineered domain-specific language (DSL),
  constraining the space of allowed programs and imparting
  prior knowledge of the domain.
  We contribute a program learning algorithm
  called \system
  that infers a DSL
  and trains a neural network to
  efficiently search for programs in the learned DSL.
  We use our model to build circuits,
  edit strings, do symbolic regression,
  and synthesize Lisp-style functions on lists,
  in each case showing that
  \system learns a domain-specific vocabulary for expressing programs.

@@

\begin{figure}\centering
\includegraphics[width = 3.5cm]{figures/regression.eps} 
  \includegraphics[width = 7cm]{figures/list.eps}
  \includegraphics[width = 3.5cm]{figures/textLearningCurve.eps}        
  \includegraphics[width = 3.5cm]{figures/circuitLearningCurve.eps}  
  \caption{Learning curves for \system both with (blue) and without (red) the recognition model as the frontier size is varied (solid/dashed/dotted lines).}\label{learningCurves} 
\end{figure}

 \section{Related Work}
 Our work is far from the first to learn to learn programs,
 an  idea that goes back to Solomonoff~\cite{solomonoff1989system}:
